ABC Group Level Fits

### 2024-01-11 Model/abc_hier.qmd
indv script ready to run

>>>>

# learning curve code
nbins <- 10
maxT <- 200
t <- dg[trial<=maxT] %>% .[,Block:=cut(trial,breaks=seq(1,maxT+(nbins-2),nbins),include.lowest=TRUE,labels=FALSE),by=id] %>%
 .[,c("id","agebin","nth_play","trial","Block","Rt","rt.max.5s","gameState","ng1","gsum1","gameState3","ng3","gsum3")]
t[, trial_perc_bin := cut(trial/max(trial), breaks = seq(0, 1, .1), include.lowest = TRUE), by = id]
#

input_layer =  c(100,350,600,800,1000,1200)
output_layer = input_layer
return_dat="train_data, test_data"
data <- ds |> filter(id==1) 
train_idx <- which(data$expMode2=="Train")
test_idx <- which(data$expMode2=="Test")

kde_results <- purrr::map(group_posterior_all, ~purrr::map_if(.x, is.list, ~compute_kde(.x$c, .x$lr, ngrid = 100, nsamples=100)))

sim_data <- sim_data_gen_s(data,input_layer,output_layer,full_sim_exam, kde_results$abc_ev$te_results$kde_samples, return_dat)

simulated = as_vector(sim_data[,1])
observed=data

dist_mean_sd <- function(simulated, observed) {
  # Calculate the means and standard deviations for simulated and observed data

  d <- tibble(observed,pred=simulated) 
  nbins <- 4
  dtrain <- d |> filter(expMode2=="Train") |> 
  mutate(Block=cut(tr,breaks=seq(1,max(tr), length.out=nbins+1),include.lowest=TRUE,labels=FALSE))

  sum_stat_train <- dtrain |> group_by(Block,x) |> summarise(mean_sim=mean(pred),sd_sim=sd(pred),mean_obs=mean(y),sd_obs=sd(y), mean_dif = mean_obs-mean_sim, sd_dif = sd_obs-sd_sim)

  sum_stat_test <- d |> filter(expMode2=="Test") |> group_by(x) |> summarise(mean_sim=mean(pred),sd_sim=sd(pred),mean_obs=mean(y),sd_obs=sd(y), mean_dif = mean_obs-mean_sim, sd_dif = sd_obs-sd_sim)

  train_mean_rmse <- sqrt(mean((sum_stat$mean_dif^2)))
  train_sd_rmse <- sqrt(mean((sum_stat$sd_dif^2)))

  test_mean_rmse <- sqrt(mean((sum_stat_test$mean_dif^2)))
  test_sd_rmse <- sqrt(mean((sum_stat_test$sd_dif^2)))

  return(tibble::lst(train_mean_rmse,test_mean_rmse))

}
